---
title: "Python Runtime Audit"
output: 
  html_document:
    theme: lumen
rmd_output_metadata:
  rsc_output_files:
    - "python-runtime-audit.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## List all content items with an unsupported version of Python

**Starting in RStudio Connect version 2022.03.0, the minimum version of Python is 3.5.** 

Use this report to identify all content using an unsupported Python version.

To pull a complete list of the content items on your Connect server, you must use an API key generated from an Admin account. Publisher account API keys will only return content items which the publisher user has been given access to view or edit.

Requirements:

- [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"}
- RStudio Connect server URL

```{r include=FALSE}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
df_full <- unnest_wider(tibble::tibble(dat = content(result)), dat) 
```

### Explore the content list

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(reactable)

# Filter the full response to select specific fields for viewing
df_view <- df_full %>%
  select(name, title, dashboard_url, app_mode, access_type, py_version, created_time, last_deployed_time) %>%
  filter(py_version < 3.5)

# Use reactable to create a nicely formatted table
reactable(df_view, searchable = TRUE, highlight = TRUE, columns = list(
  name = colDef(name = "Name"),
  title = colDef(name = "Title"),
  dashboard_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    }),
  app_mode = colDef(name = "Type"),
  access_type = colDef(name = "Access Level"),
  py_version = colDef(name = "Python Version"),
  created_time = colDef(name = "Created", format = colFormat(datetime = TRUE)),
  last_deployed_time = colDef(name = "Last Deployed", format = colFormat(datetime = TRUE))
))
```

### Download this report

```{r include=FALSE}

# Write the full content list reponse out to a CSV file for download
write.csv(df_view, "python-runtime-audit.csv", row.names=FALSE)
```

- Report: [python-runtime-audit.csv](python-runtime-audit.csv)

### Learn more about the RStudio Connect Server APIs

- [Server API Doc Reference](https://docs.rstudio.com/connect/api/)
- [Server API Cookbook](https://docs.rstudio.com/connect/cookbook/)