---
title: "Python Runtime Audit"
output: 
  html_document:
    theme: lumen
rmd_output_metadata:
  rsc_output_files:
    - "python-runtime-audit.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }` `r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }` `r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## List all content items with an unsupported version of Python

**Starting in RStudio Connect version 2022.03.0, the minimum version of Python is 3.5**

After performing this upgrade:

- Configuration files that include Python 2, or Python 3 versions prior to 3.5, will cause an error during Connect startup.
- Existing R Markdown reports and Jupyter Notebooks that use older Python versions can still be viewed. However, they cannot be deployed to Connect or re-rendered.
- Existing applications and APIs that use older Python versions will no longer run. An HTTP 502 error will be returned for all requests to these applications.

Before you begin an upgrade to RStudio Connect 2022.03.0, we recommend taking the following actions:

- Set a [System Message](https://docs.rstudio.com/connect/admin/server-management/#system-messages) on the server to warn Publishers about your upgrade timeline and the breaking change.
- Use this report to identify all content using an unsupported Python version.
- Contact any users who have content that will break due to this upgrade. 
- Let publishers know that content can be re-published to the same location with Python 3.5+, preserving existing settings like environment variables, access permissions, or runtime settings.
- Any scheduled reports that continue to run will send error emails, so we recommend turning off the scheduler or re-publishing the content with Python 3.5+.

---

To pull a complete list of the content items on your Connect server, you must use an API key generated from an Admin account. Publisher account API keys will only return content items which the publisher user has been given access to view or edit.

Requirements:

-   [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"}
-   RStudio Connect server URL

```{r include=FALSE}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
df_full <- unnest_wider(tibble::tibble(dat = content(result)), dat) 
```

### Explore the content list

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)

# Filter the full response to select specific fields for viewing
df_view <- df_full %>%
  select(name, title, dashboard_url, app_mode, access_type, py_version, created_time, last_deployed_time, owner_guid) %>%
  filter(py_version < 3.5)

# Request a page of up to 25 users.
resp <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/users?page_size=25"),
  add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
)
payload <- content(resp)

payload_list <- list()
# While the current page has results, add its contents to the list holder
# then advance to the next page.
while(length(payload$result) > 0) {

  payload_list[[length(payload_list) + 1]] <- payload$results

  # get the next page
  nextPage <- payload$current_page + 1
  resp <- GET(
    paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/users?page_size=25&page_number=", nextPage),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
  )
  payload <- content(resp)
}

# Unnest the list of lists into a single column tibble of lists
users_list <- unnest_longer(tibble::tibble(dat = payload_list), dat) 

# Rectangle the tibble of lists into a tibble of usable column data
df_users <- unnest_wider(users_list, dat)

# Match owner_guid from df_view to the users guid
df_owners_view <- df_view %>%
  left_join(df_users, by=c('owner_guid' = 'guid')) %>%
  select(name, title, dashboard_url, app_mode, access_type, py_version, last_deployed_time, owner_guid, username)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(reactable)

# Use reactable to create a nicely formatted table
reactable(df_owners_view, searchable = TRUE, highlight = TRUE, columns = list(
  name = colDef(name = "Name"),
  title = colDef(name = "Title"),
  dashboard_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    }),
  app_mode = colDef(name = "Type"),
  access_type = colDef(name = "Access Level"),
  py_version = colDef(name = "Python Version"),
  last_deployed_time = colDef(name = "Last Deployed", format = colFormat(datetime = TRUE)),
  owner_guid = colDef(name = "Owner"),
  username = colDef(name = "Username")
))
```

### Download this report

```{r include=FALSE}

# Write the full content list to a CSV file for download
write.csv(df_owners_view, "python-runtime-audit.csv", row.names=FALSE)
```

[python-runtime-audit.csv](python-runtime-audit.csv)

<br>

### Gather content owner contact information

To contact content owners ahead of upgrading to 2022.03.0, use the `/v1/users` API to enumerate all users, then join/match the user `guid` to the content `owner_guid`.

<br>

#### Summary Table: Content owners and number of content items

```{r echo=FALSE, message=FALSE, warning=FALSE}
#library(httr)
#library(tidyr)

# Summarize 
summary_tbl <- df_view %>%
  group_by(owner_guid) %>%
  summarise(count = n()) %>%
  left_join(df_users, by=c('owner_guid' = 'guid')) %>%
  select(first_name, last_name, username, count, email, user_role, locked)

knitr::kable(summary_tbl)
```

<br>

### Additional Considerations

**Documentation:**

-   [Server API Doc Reference](https://docs.rstudio.com/connect/api/)
-   [Server API Cookbook](https://docs.rstudio.com/connect/cookbook/)

#### Delete a Content Item

The RStudio Connect Server API can also be leveraged to delete a content item. Deleting content is a destructive operation and cannot be reversed. 

Use the [`DELETE /v1/content/{guid}`](https://docs.rstudio.com/connect/api/#delete-/v1/content/{guid}) endpoint. A successful request will return a 204 HTTP status code with an empty response.

**Example:** 
```
curl --silent --show-error -L --max-redirs 0 --fail -X DELETE \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    "${CONNECT_SERVER}__api__/v1/content/ccbd1a41-90a0-4b7b-89c7-16dd9ad47eb5"
# =>
```

