---
title: "Shiny Application Usage Report"
output: 
  html_document:
    theme: united
---

`r gitlink::ribbon_css("https://github.com/kellobri/rsc-admin-showcase", text="EXAMPLE CONTENT", color = 'red', fade = FALSE)`

Connect records visits to Shiny applications and lets you see:

* Which applications were viewed
* When the applications were viewed
* Who viewed the application
* The length of each session

Details about each visit are available through the [Instrumentation APIs](https://docs.rstudio.com/connect/api/#tag--Instrumentation). Use these records to perform your own analysis. 

Code examples showing how to access the instrumentation data are in the [User Activity](https://docs.rstudio.com/connect/cookbook/user-activity/) recipes within the RStudio Connect API Cookbook.

## Report on Shiny Usage over the last 28 Days

**Time Windows**

This API accepts optional from and to timestamps to define a window of interest. If from is not specified, it is assumed to be before the earliest recorded information. If to is not specified, it is assumed to be "now".

Any visit to content that falls inclusively within the time window will be part of the result set.

_The information returned is based on data collected by RStudio Connect as users visit Shiny applications. Because of how visits are detected, end times will be slightly inflated by a reconnect timeout, generally around 15 seconds._

```{r include=FALSE}
library(connectapi)
library(dplyr)
library(ggplot2)
library(lubridate)
library(ggthemes)

# Connect to the server
client <- connect()

# Get Shiny usage data for the last 28 days
from <- Sys.Date() - lubridate::days(28)
usage <- get_usage_shiny(client, from = from, limit = Inf) %>%
  mutate(
    started = lubridate::ymd_hms(started),
    ended = lubridate::ymd_hms(ended),
    session_duration = ended - started
  ) %>%
  filter(session_duration > lubridate::dseconds(5))

# Get all users
all_users <- get_users(client, page_size = 500)

# Get all content
all_content <- get_content(client)
```


### Top Applications 

The top 5 applications over the last 28-day period. 

```{r echo=FALSE}
# Calculate the applications with the most sessions
top_apps <- usage %>% 
  group_by(content_guid) %>% 
  summarize(visits = n()) %>% 
  arrange(desc(visits)) %>% 
  head(5) %>%
  mutate(name = purrr::map_chr(content_guid, ~ content_title(client, .x)))

# Show top applications in a plot
top_apps %>% 
  {ggplot(., aes(reorder(stringr::str_wrap(name, 30), visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_economist() +
     labs(
       y = "# of Shiny Sessions",
       x = NULL
     )}
```

#### Application Details

```{r echo=FALSE}
library(reactable)

# Provide Links to the Top Apps
app_info <- top_apps %>%
  left_join(all_content, by = c("content_guid" = "guid")) %>%
  rename(guid = content_guid) %>%
  left_join(all_users, by = c(owner_guid = "guid")) %>%
  mutate(link_title = paste('<a href="',dashboard_url,'">',title,'</a>', sep = "")) %>%
  select(guid, username, link_title, app_mode)
  
reactable::reactable(app_info,
                     columns = list(
                       guid = colDef(name = "Content GUID"),
                       username = colDef(name = "Owner"),
                       link_title = colDef(name = "Title", html = T),
                       app_mode = colDef(name = "App Mode")
                     ))
```


## Shiny Sessions Over Time

```{r echo=FALSE}
usage %>% mutate(day = round_date(started, "day")) %>% 
    group_by(day) %>% 
    summarise(visits = n()) %>% 
    arrange(desc(visits)) %>% 
    {ggplot(., aes(day, visits)) + 
     geom_bar(stat = "identity") + 
     theme_economist() +
     labs(
       y = "# of Shiny Sessions",
       x = NULL
     )}
```

## Shiny Sessions by User (Top 5)

```{r echo=FALSE}
usage %>%
    group_by(user_guid) %>% 
    summarise(visits = n()) %>% 
    left_join(all_users, by = c(user_guid = "guid")) %>%
    mutate(username = coalesce(username, "anonymous")) %>%
    select(username, visits) %>% 
    arrange(desc(visits)) %>% 
    head(5) %>% 
    {ggplot(., aes(reorder(username, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_economist() +
     labs(
       y = "Number of Shiny Sessions",
       x = NULL
     )}
```

