---
title: "Content Permissions Audit"
output: 
  html_document:
    theme: lumen
---

`r gitlink::ribbon_css("https://github.com/kellobri/rsc-admin-showcase", text="EXAMPLE CONTENT", color = 'red', fade = FALSE)`

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## First: List all content items on the RStudio Connect server

To pull a complete list of the content items on your Connect server, you must use an API key generated from an Admin account. Publisher account API keys will only return content items which the publisher user has been given access to view or edit.

Requirements:

- [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"}
- RStudio Connect server URL

```{r include=FALSE}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
df_full <- unnest_wider(tibble::tibble(dat = content(result)), dat) 
```

---

## Then: Get Content Permissions Lists

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(lubridate)

# Filter down to content created in the last year
df_recent <- df_full %>%
  filter(created_time >= today() - years(1))

# Filter down to content with access_type = acl
acl_content <- df_recent %>%
  filter(access_type == 'acl')

# Function for initializing an empty permissions tibble
empty_permissions <- function() {
  cols <- c('id','content_guid','principal_guid','principal_type','role')
  cols %>% purrr::map_dfc(setNames, object = list(character()))
}

# Function for calling the content `/permissions` API endpoint
get_permissions <- function(guid) {
  permissions <- GET(paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content/",guid,"/permissions"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))
  
  if (status_code(permissions) == 200){
    result <- tidyr::unnest_wider(tibble::tibble(dat = content(permissions)), dat)
    if (dim(result)[1] == 0){
      empty_permissions() 
    } else {
      result
    }
  } else {
    empty_permissions()
  }
}

# Get permissions for all ACL-type content items
# Content that is accessible only by the publisher-owner (no additional users or groups) will return no records
acl_info <- purrr::map(acl_content$guid, get_permissions)
acl_tibble <- tidyr::unnest(tibble::tibble(dat = acl_info), dat)

```


```{r message=FALSE, warning=FALSE}
# Get User and Groups Information

library(pins)
board <- board_rsconnect()

# Retrieve Users and Groups Pins
users <- board %>% pin_read("kelly.obriant/user-info")
groups <- board %>% pin_read("kelly.obriant/group-info")

# Join acl_tibble with user names
prin_user <- acl_tibble %>% 
  filter(principal_type == 'user') %>%
  left_join(users, by=c("principal_guid" = "guid")) %>%
  left_join(df_recent, by=c("content_guid" = "guid")) %>%
  select(username, role, name, title, content_url)

# Join acl_tibble with group names
prin_group <- acl_tibble %>%
  filter(principal_type == 'group') %>%
  left_join(groups, by=c("principal_guid" = "guid")) %>%
  left_join(df_recent, by=c("content_guid" = "guid")) %>%
  select(name.x, role, name.y, title, content_url)

```

## Users Access Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(reactable)

# Use reactable to create a nicely formatted table
reactable(prin_user, searchable = TRUE, highlight = TRUE, columns = list(
  username = colDef(name = "Username"),
  role = colDef(name = "Role Permissions"),
  name = colDef(name = "Content Name"),
  title = colDef(name = "Content Title"),
  content_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    })
))
```

## Groups Access Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(reactable)

# Use reactable to create a nicely formatted table
reactable(prin_group, searchable = TRUE, highlight = TRUE, columns = list(
  name.x = colDef(name = "Group Name"),
  role = colDef(name = "Role Permissions"),
  name.y = colDef(name = "Content Name"),
  title = colDef(name = "Content Title"),
  content_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    })
))
```